R Tools for Obspack, Receptors and Footprints (rtorf)

### 2025-02-13 README.Rmd
adding some legacy code
README

```{r install, eval = F}
remotes::install_github("noaa-gml/rtorf")
```

@@

I'm currently implementing a version in python:

@@

>>>>

Using git bash/powershell
```{bash installb, eval = F}
git clone https://github.com/noaa-gml/rtorf
R CMD INSTALL rtorf
```

Using remotes R package
```{r install, eval = F}
remotes::install_github("noaa-gml/rtorf")
```

@@

I'm currently implementing a version in python [pytorf](https://github.com/noaa-gml/pytorf):

@@

```
## Special thanks to all the contributors

[![Contributors](https://contrib.rocks/image?repo=noaa-gml/rtorf)](https://github.com/noaa-gml/rtorf/graphs/contributors)
